CKY Parsing With Independence Constraints

### 2015-07-03 paper.tex
Mention appendix

The results of running the parser on section 22 using the linear classifier from
Section \ref{sec:linear-classifier} are shown in Table
\ref{tbl:parse-results}. The table shows the total time taken, the total
times entering the inner loop, the F$_{\text{1}}$ and difference from the baseline, and the
number of times the parse failed using the constraints. The parser with
independence constraints saves 38\% of the computation inside the CKY loop over
the baseline, corresponding to about 20\% reduction in total parse time (12\% if
the running time of the classifier is included), at the cost of a 2-point drop
in F-score.

@@

\section{Detailed parse results}
\label{sec-8-2}

>>>>

The results of running the parser on section 22 using the linear classifier from
Section \ref{sec:linear-classifier} are shown in Table \ref{tbl:parse-results}.
The table shows the total time taken, the total times entering the inner loop,
the F$_{\text{1}}$ and difference from the baseline, and the number of times the
parse failed using the constraints. The parser with independence constraints
saves 38\% of the computation inside the CKY loop over the baseline,
corresponding to about 20\% reduction in total parse time (12\% if the running
time of the classifier is included), at the cost of a 2-point drop in F-score.
Detailed results of further experiments with various thresholds on sentence
length and classifier score are shown in Appendix~\ref{sec:parse-results-full}.

@@

\section{Detailed parse results}
\label{sec:parse-results-full}
\label{sec-8-2}
